Manuscript

### 2014-08-08 inst/simulation/manuscript.Rmd
...

```{r figure-3}
validation <- Validation()
populationSizes.temporal <- validation$getValidationTemporalPopulationSizes(modelNames=modelNames)

p <- ggplot(populationSizes.temporal, aes(Observed, Estimated)) + geom_point() + stat_smooth(method="lm", colour="black") +
  geom_abline(colour="darkgrey") + facet_wrap(~Scenario, scales="free") +
  theme_minimal() + theme(panel.border=element_rect(fill="transparent"))
print(p)
saveFigure(p, "manuscript-figure-3.png", width=8, height=4)
```

```{r figure-4}
validation <- Validation()
populationSizes.spatial <- validation$getValidationSpatialPopulationSizes(modelNames=modelNames)

>>>>

```{r figure-3}
study <- getStudy(scenario="A")
validation <- Validation(study=study)
populationSizes <- validation$getValidationTemporalPopulationSizes(modelNames=modelNames)

p <- ggplot(populationSizes, aes(Observed, Estimated)) + geom_point() + stat_smooth(method="lm", colour="black") +
  geom_abline(colour="darkgrey") + facet_wrap(~Scenario, scales="free") +
  theme_minimal() + theme(panel.border=element_rect(fill="transparent"))
print(p)
saveFigure(p, "manuscript-figure-3.png", width=8, height=4)
```

```{r figure-4}
study <- getStudy(scenario="A")
validation <- Validation(study=study)
populationCorrelations <- validation$getValidationSpatialPopulationSizes(modelNames=modelNames)
p <- ggplot(populationCorrelations, aes(True, Correlation)) + geom_point() + facet_wrap(~Scenario) +
  theme_minimal() + theme(panel.border=element_rect(fill="transparent"))
print(p)
saveFigure(p, "manuscript-figure-4.png", width=8, height=4)
```

```{r figure-5}
study <- getStudy(scenario="A")
validation <- Validation(study=study)
credibilityIntervals <- validation$getValidatedCredibilityIntervalsProportions(modelNames=modelNames)
